
%-------------------------
% Author : Isin Altinkaya
% Website: https://github.com/isinaltinkaya/cv
%------------------------

\documentclass[letterpaper,10.5pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{graphicx}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}


\usepackage{xcolor}
\usepackage[pdftex]{hyperref}

\hypersetup{
    colorlinks = true,
    linkcolor = MidnightBlue,
    anchorcolor = blue,
    citecolor = blue,
    filecolor = blue,
    urlcolor = BlueViolet
}

    
% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large 
}{}{1em}{}[\color{black}\titlerule \vspace{-3pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{3pt} \\
    #5
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

%\renewcommand{\labelitemii}{$\circ$}
%\renewcommand{\labelitemii}{$\rightarrow$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%
%\newcommand\textline[4][t]{%
%  \par\smallskip\noindent\parbox[#1]{.333\textwidth}{\raggedright\texttt#2}%
%  \parbox[#1]{.333\textwidth}{\centering#3}%
%  \parbox[#1]{.333\textwidth}{\raggedleft\texttt{#4}}\par\smallskip%
%}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\href{http://isinaltinkaya.com/}{isinaltinkaya.com} \hfill \begin{Huge}I\c{s}{\i}n Alt{\i}nkaya \end{Huge} \\
\href {https://github.com/isinaltinkaya}{github/isinaltinkaya} \hfill Oester Voldgade 5-7 1350 \\
\href {https://twitter.com/isinaltinkaya}{twitter/isinaltinkaya}  \hfill Copenhagen K, Denmark \\
\href{mailto:isinaltinkaya@gmail.com}{isinaltinkaya@gmail.com} $\sbullet[.5]$ \href{mailto:isin.altinkaya@sund.ku.dk}{isin.altinkaya@sund.ku.dk} \hfill (+45) 501-186-79 \\



%-----------PERSONAL-----------------
%\section{Personal}
%\textbf{Date of Birth:} 15 October 1996
 
 
%-----------LANGUAGE-----------------
\section{Language}
Turkish \textit{(Native)} \hfill English \textit{(Fluent)} \hfill German \textit{(Beginner)} \hfill Danish \textit{(Beginner)} 

%\quad \small TOEFL iBT: 102/120 (Reading: Advanced, Listening: Advanced, Speaking: High-Intermediate, Writing: Advanced) \\

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PhD} {University of Copenhagen, Denmark}
      {Faculty of Health and Medical Sciences} {2022/1 - expected in 2025/1}
    \quad \textbf{Title:} Statistical methods for population genetic inference based on low-depth sequencing data \\
    \quad \textbf{Advisors:} Thorfinn S. Korneliussen and Rasmus Nielsen
    \resumeSubheading
      {BSc in Biology} {Hacettepe University, Ankara, Turkey}
      {Faculty of Science, Department of Biology} {2020/7}
%    \quad GPA: 3.23, \quad Certificate No: 20-321-032
  \resumeSubHeadingListEnd






%-----------RESARCH EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Globe Institute, Section for GeoGenetics}{University of Copenhagen, Denmark}
      {Research assistant, Advisors: Thorfinn S. Korneliussen and Rasmus Nielsen}{2020/10 - 2021/12}
      {Contributed to a number of independent projects which resulted in 2 publications and 3 manuscripts in preparation. Worked on the development and evaluation of the Lundbeck center bioinformatics pipeline processing thousands of ancient genomes. }
    \medskip
    
    
    \resumeSubheading
      {Fumagalli Lab}{Imperial College London, United Kingdom}
      {Intern, Advisor: Matteo Fumagalli}{2019/7 - 2019/9}
      {Contributed to the HMMPloidy project by implementing various methods, including the genotype likelihood estimation for any N-ploidy, which resulted in a publication. Funded by Erasmus+ Traineeship Grant.}
    \medskip


    \resumeSubheading
      {Biogeography Research Laboratory}{Hacettepe University, Turkey}
      {Intern, Advisor: Bar{\i}\c{s} \"{O}z\"{u}do\u{g}ru}{2019/2 - 2020/7}
      {Developed a snakemake-based bioinformatic pipeline for the processing and phylogenomic analyses of RADSeq data, which resulted in a manuscript in preparation.}
    \medskip
 
    \resumeSubheading
      {Laboratory of Comparative and Evolutionary Biology}{Middle East Technical University, Turkey}
      {Intern, Advisor: Mehmet Somel}{2018/8 - 2019/6}
      {Carried out analyses to evaluate the effects of the properties of probe sequences in the 1240K SNP capture method.}

    \medskip


    \resumeSubheading
      {Laboratory of Evolutionary and Quantitative Genetics}{Hacettepe University, Turkey}
      {Intern, Advisor: Ergi Deniz \"{O}zsoy}{2015/10 - 2018/12}
      {Contributed to the statistical analyses of quantitative genetics projects based on Drosophila Genetic Reference Panel 2 (DGRP2) data, which resulted in a poster presentation and acknowledgments in two MSc and one PhD thesis.}
  \resumeSubHeadingListEnd
  


%----------- PUBLICATIONS------------
\section{Publications}


\textbf{[2]} \hspace{0.42cm} Alex Mas-Sandoval, Nathaniel S. Pope, Knud Nor Nielsen, \textbf{Isin Altinkaya}, Matteo Fumagalli, and Thorfinn Sand Korneliussen. \href{https://doi.org/10.1093/gigascience/giac032}{Fast and accurate estimation of multidimensional site frequency spectra from low-coverage high-throughput sequencing data.} \textit{GigaScience} (2022).

\smallskip


\textbf{[1]} \hspace{0.42cm} Samuele Soraggi, Johanna Rhodes, \textbf{Isin Altinkaya}, Oliver Tarrant, François Balloux, Matthew C. Fisher, Matteo Fumagalli. \href{https://doi.org/10.24072/pcjournal.178}{HMMploidy: inference of ploidy levels from short-read sequencing data.} \textit{Peer Community Journal} (2022).\\
\medskip

\hspace{0.2cm} \textbf{Preprints} \\
\medskip

$\sbullet[.6]$ \hspace{0.74cm}  Morten E. Allentoft [et al, including \textbf{Isin Altinkaya}.]  \href{https://www.biorxiv.org/content/10.1101/2022.05.04.490594v5}{Population Genomics of Stone Age Eurasia}, \textit{bioRxiv}, (2022).\\

\medskip

\hspace{0.2cm} \textbf{Manuscripts in preparation} \\
\medskip


$\sbullet[.6]$ \hspace{0.74cm}  \textbf{Isin Altinkaya}, Emrullah Y{\i}lmaz, Ismail Kudret Saglam, Bar{\i}\c{s} \"{O}z\"{u}do\u{g}ru. Understanding the phylogenetic relationships within the Noccaea species complex from RADseq data using the multi-species coalescent. \\

\smallskip
$\sbullet[.6]$ \hspace{0.74cm}  \textbf{Isin Altinkaya}, Lei Zhao, Rasmus Nielsen, Thorfinn S. Korneliussen. A Genotype Likelihood Framework for Analysis of Molecular Variance (AMOVA) with Low Depth Sequencing Data. \\

\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Hugh McColl, Jos\'e Victor Moreno Mayar, \textbf{Isin Altinkaya}, Thorfinn Sand Korneliussen, Accurate and precise library complexity estimations for ancient DNA libraries using patterned flowcell technology. \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Fulya E. Yediay [et al, including \textbf{Isin Altinkaya}.]  Population genomics of Bronze Age Mediterranean. \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Hugh McColl [et al, including \textbf{Isin Altinkaya}.]  Population genomics of Iron Age. \\



%--------SKILLS------------
\section{Skills}
\textbf{Programming languages}: C, C++, R, Python, Java, Perl, Rust \\
\textbf{Scripting and typesetting}: \LaTeX, Markdown, HTML\&CSS, JavaScript, Google Apps Script, sed, awk, Bash \\
\textbf{Operating systems}: GNU/Linux \\
\textbf{Other tools and frameworks}: Git, Conda, Snakemake, RShiny, Dash, Django, Make \\


% %-----------SELECTED COURSES-----------------
% \section{Relevant Courses}

% \textbf{Computational Statistics}, University of Copenhagen, Department of Mathematical Sciences, (2022) \\
% \textbf{Advanced Topics in Data Analysis}, University of Copenhagen, (2021) \\
% \textbf{Fundamentals in Computational Analysis of Large-Scale Datasets}, University of Copenhagen, (2021) \\
% \textbf{Stay-at-Home RevBayes Workshop}, Topics: Tree inference from molecular data, evaluating MCMC performance, assessing model adequacy and macroevolutionary analyses, (2020) \\
% \textbf{Fundamentals of Bioinformatics}, Department of Computer Science, Hacettepe University, Lect.: Tunca Do\u{g}an, (2019) \\
% \textbf{Population Genetics}, Graduate course, Department of Molecular Biology and Genetics, Middle East Technical University, Lect.: Mehmet Somel, (2018) \\
% \textbf{Population Genetics Simulations with R}, Middle East Technical University, (2018) \\
% \textbf{Introduction to Game Theory}, Anadolu University, (2017) \\
% \textbf{Evolutionary Genomics Winter School}, Hacettepe University, (2017) \\


%-----------PRESENTATIONS-----------------
\section{Conferences, Workshops, and Talks}
%ADD 12 april 23 epic 

\medskip
\textbf{Oral Presentations}
\medskip

\textbf{[5]} \hspace{0.42cm} {A Genotype Likelihood Framework for the Analysis of Molecular Variance (AMOVA)}, \textit{Evolution and Population Genetics in Denmark (EPIC) Conference}, Denmark, (2022). \\
\smallskip
\textbf{[3]} \hspace{0.42cm} {Biological Evolution}, \textit{Science and Future Magazine Science for Youth Seminar}, Turkey, (2018). \\
\smallskip
\textbf{[4]} \hspace{0.42cm} {Evolutionary Biology and Preventing the Species Extinction}, \textit{7th National Environment and Ecology Student Congress}, Turkey, (2016). \\
\smallskip
\textbf{[2]} \hspace{0.42cm} {Evolutionary Biology and Environmental Problems}, \textit{Turkey Meets Evolution: Bilkent University}, Turkey, (2016). \\
\smallskip
\textbf{[1]} \hspace{0.42cm} {Evolutionary Biology and Preventing the Species Extinction}, \textit{7th National Environment and Ecology Student Congress}, Turkey, (2016). \\

%-----------POSTER PRESENTATIONS-----------------
%\section{Poster Presentations}
\medskip
\textbf{Poster Presentations}
\medskip

\textbf{[2]} \hspace{0.42cm}  \textbf{Isin Altinkaya}, Lei Zhao, Rasmus Nielsen, Thorfinn S. Korneliussen. A Genotype Likelihood Framework for Analysis of Molecular Variance, $d_{xy}$ and Neighbor-Joining Trees with Low Depth Sequencing Data. \textit{Society for Molecular Biology and Evolution (SMBE)}, Italy, (2023). \\


\textbf{[1]} \hspace{0.42cm} Damla Aygün, \textbf{Isin Altinkaya}, Murat Y{\i}lmaz, Ergi Deniz \"{O}zsoy, Efe Sezgin. Host genetics of microbiota diversity in \textit{Drosophila melanogaster}. \textit{Ecology and Evolutionary Biology Symposium (EEBST)}, Turkey, (2018). \\
%i analysed Drosophila melanogaster microbial dataset to test the diversity using various diversity indices using R package named vegan


%-----------TEACHING EXPERIENCE------------

\section{Teaching Experience}

$\sbullet[.6]$ \hspace{0.74cm}  Advanced Bioinformatics for NGS, Graduate course, \textbf{Teaching Assistant}, University of Copenhagen, (2021). \\
$\sbullet[.6]$ \hspace{0.74cm}  Introduction to Computational Biology and Bioinformatics, \textbf{Teaching Assistant}, Hacettepe University, (2020).\\
$\sbullet[.6]$ \hspace{0.74cm}  Biometry, 4th year elective course, Hacettepe University, \textbf{Teaching Assistant}, (2019). \\
%I worked as a teaching assistant and contributed by preparing exercises and teaching the basics of statistical analyses and visualization using R 
$\sbullet[.6]$ \hspace{0.74cm}  Introductory Evolutionary Biology, Science and Utopia Magazine Evolution Courses, \textbf{Lecturer}, (2017). \\
$\sbullet[.6]$ \hspace{0.74cm}  Introduction to Evolution, Hacettepe University Evolution Workshops, \textbf{Lecturer}, (2016). \\



%-----------SELECTED SYMPOSIUM AND EVENTS------------
%\section{Other Academic Achievements, Honors, and Activities}
\section{Scientific Outreach, Public Engagement and Activities}

Contributed to the organization of various free symposiums, workshops, and events focusing on teaching evolution and scientific thinking to the public, with a special focus on underdeveloped regions. \\

\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  12th Aykut Kence Evolution Conference, \textbf{Organizer}, (2018). \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Science and Utopia Magazine, \textbf{Popular science writer}, Subject: Evolutionary biology, (June 2017 - May 2018). \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Popular Science Magazine, Turkey branch, \textbf{Popular science news editor and translator}, (February - May 2016). \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  \href{https://evrimagaci.org/isinaltinkaya/}{Tree of Evolution}, \textbf{Writer and editor}; Subject: Evolutionary biology, (November 2015 - present).\\
Authored multiple popular science articles, which can be found at \href{https://evrimagaci.org/isinaltinkaya/}{evrimagaci.org/isinaltinkaya}.

\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Turkey Meets Evolution: Izmir, \textbf{Organizer}, (2012). \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Tree of Evolution Bornova Anatolian High School Evolution Conference, \textbf{Organizer}, (2012). \\
\smallskip

%-----------POPULAR PUBLICATIONS------------
\textbf{Popular Science Publications in Magazines (in Turkish)}


\medskip

$\sbullet[.6]$ \hspace{0.74cm}  Science and Utopia Magazine, Issue: 283, Examining the thin line between living and non-living matter, co-authored with Martin Hanczyc.\\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Science and Utopia Magazine, Issue: 278, Education and perceptions: Evolution in Turkey. \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Atheist Magazine, Issue: 16, The evolving brain. \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Atheist Magazine, Issue: 14, Evolutionary biology and LGBTI+ in nature. \\
\smallskip

$\sbullet[.6]$ \hspace{0.74cm}  Atheist Magazine, Issue: 13, Understanding evolution through the human body. \\
\smallskip

%\textbf{[1]} \hspace{0.42cm} Atheist Magazine, Issue: 12, Atheist thinking under the light of evolution. \\
%\smallskip

\section{Open Source Contributions}

\textbf{[10]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/gptchatteR}{gptchatteR} : An experimental R package for interacting with OpenAI GPT models in R. It provides a framework for using AI language models to help learning and conducting data analysis, plotting and data wrangling from R console. (2023). \\
\smallskip

\textbf{[9]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/google-slides_scripts}{gs\_scripts} : Custom scripts providing various additional functionalities to Google Slides (2022). \\
\smallskip

\textbf{[8]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/vcfgl}{vcfgl} : A tool for fast and efficient simulation of genotype likelihoods from VCF GT tags (2022). \\
\smallskip

\textbf{[7]} \hspace{0.42cm} \href{https://github.com/ANGSD/angsd}{ANGSD} : Actively contributing to the development and maintenance of the ANGSD software. (2021 - ongoing).\\
\smallskip

\textbf{[6]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/bash-functions}{bash-functions} : Custom functions designed for bashrc to perform various tasks, including runda (environment-safe wrapper for conda), treemd (format and print the tree structure of a git repository for markdown), lns (easy and safe wrapper for creating symbolic links) (2021).

\textbf{[5]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/i3pomodoror}{i3pomodoror} : i3blocks wrapper for the R package pomodoror (2020). \\
\smallskip

\textbf{[4]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/PopulasyonBuyumesi}{PopulasyonBuyumesi} : An RShiny application for teaching population ecology, including population growth simulations and interactive plots. The RShiny app is available at \href{https://isinaltinkaya.shinyapps.io/PopulasyonBuyumesiSimulasyonlari/}{isinaltinkaya.shinyapps.io/PopulasyonBuyumesiSimulasyonlari/} (in Turkish), (2020).\\
\smallskip

\textbf{[3]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/cheatsheets}{cheatsheets} : Custom Markdown tutorials containing custom functions, examples, tips and tricks for using various tools and programming languages effectively, such as bash, git, jupyter, Make, conda and R (2020). \\
\smallskip

\textbf{[2]} \hspace{0.42cm} \href{https://github.com/SamueleSoraggi/HMMploidy}{HMMploidy} : A tool to calculate ploidy levels from genotype likelihoods and coverage using Hidden Markov Models. Contributed to the development of the open source software as a part of an academic project (see Publications/1), (2020).\\
\smallskip

\textbf{[1]} \hspace{0.42cm} \href{https://github.com/isinaltinkaya/i3gcalendar}{i3gcalendar} : Google Calendar i3blocks integration for i3wm (2018). \\
\smallskip


%-----------SCHOLARSHIPS & AWARDS---------------
\section{Scholarships \& Awards}
\textbf{[5]} \hspace{0.42cm} Erasmus+ Traineeship Grant, Imperial College London, (2019). \\
\textbf{[4]} \hspace{0.42cm} Hacktoberfest Award, for contributing to open source projects, (2019). \\
\textbf{[3]} \hspace{0.42cm} Hacktoberfest Award, for contributing to open source projects, (2018). \\
\textbf{[2]} \hspace{0.42cm} Atheist Alliance International Foundation Scholarship for Students in Underdeveloped Countries, (2017). \\
\textbf{[1]} \hspace{0.42cm} Atheist Alliance International Foundation Scholarship for Students in Underdeveloped Countries, (2016). \\

%-----------SOCIETY MEMBERSHIPS-----------------
%Society Memberships
\section{Memberships \& Affiliations}
Society for Molecular Biology and Evolution, \textit{2023 - present} \\
Society for the Study of Evolution, \textit{2021 - present} \\
Free Software Foundation, \textit{2020 - present} \\
Ecology and Evolutionary Biology Society of Turkey, \textit{2017 - present} \\


\end{document}  